Integrated approach to modeling to krill population dynamics in Wester Antarctic Peninsula: spatial and ecosystem considerations

### 2024-09-08 index.Rmd
add html

```{r setup1, echo=FALSE}
#rm(list = ls())
#set.seed(999)
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.height = 5,
                      fig.width = 7,
                      fig.align = 'center',
                      fig.pos = "H",
                      dev = 'jpeg',
                      dpi = 300,
                      tidy.opts=list(width.cutoff=50), 
                      tidy=TRUE)
#XQuartz is a mess, put this in your onload to default to cairo instead
options(bitmapType = "cairo") 
# (https://github.com/tidyverse/ggplot2/issues/2655)
# Lo mapas se hacen mas rapido
```

@@

#s9
base.model9 <- SS_output(dir=dir9,
                        covar=T,
                        forecast=T)

# html
SS_plots(base.model9,
         uncertainty=T,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75,
         minbthresh=0.20, 
         forecast=T)

@@

comparision between select models `No spatial`and `Spatial implicit` and `Spatial W/ new set parametres`

@@

                 "Spatial",
                 "Spatial w/ new set LH paramters"),
                 labels = c("Year", 
                            "Spawning biomass (t)",
                            "Relative spawning biomass", 
                            "Age-0 recruits (1,000s)",
                            "Recruitment deviations", 
                            "Index", "Log index", 
                            "1 - SPR", 
                            "Density",
                            "Management target", 
                            "Minimum stock size threshold",
                            "Spawning output",
                            "Harvest rate"),
                 png=TRUE,plotdir=Figs)
```

@@

comp1_9 <- SSplotComparisons(summaryoutput1_9,
                  legendlabels = c(
                                   "Base",
                 "selectivity Block 2006"),
                 labels = c("Year", 
                            "Spawning biomass (t)",
                            "Relative spawning biomass", 
                            "Age-0 recruits (1,000s)",
                            "Recruitment deviations", 
                            "Index", "Log index", 
                            "1 - SPR", 
                            "Density",
                            "Management target", 
                            "Minimum stock size threshold",
                            "Spawning output",
                            "Harvest rate"),
                 png=TRUE,plotdir=Figs)
```
## Comparsion in sd long term time series

@@

>>>>

```{r setup1, echo=FALSE}
#rm(list = ls())
#set.seed(999)
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = 'center',
                      fig.pos = "H",
                      dev = 'jpeg',
                      dpi = 300,
                      tidy.opts=list(width.cutoff=50), 
                      tidy=TRUE)
#XQuartz is a mess, put this in your onload to default to cairo instead
options(bitmapType = "cairo") 
# (https://github.com/tidyverse/ggplot2/issues/2655)
# Lo mapas se hacen mas rapido
```

@@

#s9
base.model9 <- SS_output(dir=dir9,
                        covar=T,
                        forecast=T)
```

```{r eval= FALSE, message=F, include=FALSE}
# html
SS_plots(base.model9,
         uncertainty=T,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75,
         minbthresh=0.20, 
         forecast=T)

@@

## Comparision between select models `No spatial`and `Spatial implicit` and `Spatial W/ new set parametres`

@@

                 "Spatial",
                 "Spatial w/ new set LH paramters"),
                 filenameprefix = "COM1",
                 labels = c("Year", 
                            "Spawning biomass (t)",
                            "Relative spawning biomass", 
                            "Age-0 recruits (1,000s)",
                            "Recruitment deviations", 
                            "Index", "Log index", 
                            "1 - SPR", 
                            "Density",
                            "Management target", 
                            "Minimum stock size threshold",
                            "Spawning output",
                            "Harvest rate"),
                 png=TRUE,plotdir=Figs)
```

@@

comp1_9 <- SSplotComparisons(summaryoutput1_9,
                  legendlabels = c(
                                   "Base",
                 "selectivity Block 2006"),
                 filenameprefix = "COM1_9",
                 labels = c("Year", 
                            "Spawning biomass (t)",
                            "Relative spawning biomass", 
                            "Age-0 recruits (1,000s)",
                            "Recruitment deviations", 
                            "Index", "Log index", 
                            "1 - SPR", 
                            "Density",
                            "Management target", 
                            "Minimum stock size threshold",
                            "Spawning output",
                            "Harvest rate"),
                 png=TRUE,plotdir=Figs)
```
## Comparsion in sd long term time series

@@

```
## AKL

```{r AKL, out.width='60%',  fig.cap="Representation of ALK Matrix to krill in 48.1"}
alk_matrix <- base.model1$ALK[,,1] # Ajusta las dimensiones según tu matriz

# Convertir la matriz en un data.frame
alk_df <- as.data.frame(as.table(alk_matrix))

# Renombrar columnas para mayor claridad
colnames(alk_df) <- c("Length", "TrueAge", "Value")

# Asegúrate de que las columnas Length y TrueAge sean numéricas
alk_df$Length <- as.numeric(as.character(alk_df$Length))
alk_df$TrueAge <- as.numeric(as.character(alk_df$TrueAge))

# Asegúrate de que la columna Value sea numérica
alk_df$Value <- as.numeric(alk_df$Value)

# Crear el plot usando ggplot
ggplot(alk_df, aes(x = TrueAge, y = Length, fill = Value)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "blue") +
  labs(x = "True Age",
       y = "Length",
       fill = "Value") +
  theme_bw()+
  theme(legend.position = "none")
```
